---
output:
  html_document:
    css: "www/css/modest.css"
---


```{r setup, include=FALSE, echo=FALSE}
suppressPackageStartupMessages({
  library(htmltools)
  library(vembedr)
  library(shiny)
  library(shinycssloaders)
})

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.height = 8, fig.width = 10)

AD_Link <- "https://www.youtube.com/watch?v=Z9XZ7gUKEIQ"
EducatR_Link <- "https://youtu.be/DUwFSHFnWp8"
```

### Professional Work
This section primarily highlights my contributions to ***published*** projects. Most client projects have been confidential, and not all of the software I developed is publicly available (especially R shiny apps).

#### Metrum Research Group
- I have contributed to many of the packages found at <a href="https://github.com/metrumresearchgroup" target="_blank">github.com/metrumresearchgroup</a>, relating to NONMEM model management & submission, data visualization, data summarization and formatting (exported as latex, HTML, RTF, or MS word), software validation, and R shiny.
   - I have contributed the most to [bbr](https://metrumresearchgroup.github.io/bbr/), [pmforest](https://metrumresearchgroup.github.io/pmforest/), [mpn.scorecard](https://metrumresearchgroup.github.io/mpn.scorecard/), and [mrgda](https://metrumresearchgroup.github.io/mrgda/), though I have also been closely involved with the development of [nmrec](https://metrumresearchgroup.github.io/nmrec/).
   - Each of these packages bundled together facilitate model development and submission, and are outlined in Metrum's [Expo](https://merge.metrumrg.com/expo/expo1-nonmem-foce/).
- Designed and personalized R shiny apps for internal tool development and external client needs, usually relating to PKPD simulation.
- Developed a shiny app to contain re-usable shiny modules, with the intention of creating more portable shiny code to be used in multiple client projects.
- Developed a complex shiny app to sort through and filter a database with interactive visualizations, statistical summaries, and parameterized report generation. 
- Worked on client projects within the scope of data assembly, EDA tables and figures, PK simulation, data visualization and report generation.
- Helped validate and write tests for our cloud computing platform, Metworx.

#### Certara
- <a href="https://pharmacometrics.shinyapps.io/COVID-19-CompoundScreening_TestNewUI/" target="_blank">Compound Screening Dashboard</a>, which links to other apps I worked on.
-  Note that this link may soon be changed. Will publish the offical Certara link when this happens.
- <a href="https://pharmacometrics.shinyapps.io/COVID-19-VK-MODEL/" target="_blank">Viral Kinetics Model</a>
- I helped develop other apps on <a href="https://www.covidpharmacology.com/in-silico-workbench/"  target="_blank">Certara's website</a> using the flexdashboard R package, though I wouldnt count this as R shiny experience given the R package's simplicity




### Personal Projects & Github Repositories

The following repositories illustrate some of my more recent personal coding projects:

 - [pythonR](https://barrettk.github.io/pythonR/): pythonR is an R package that facilitates the seamless integration of Python code and functionality within R environments. Leveraging the reticulate package, pythonR aims to simplify the process of developing Python-based functions in R, making it easier to set up, test, and validate Python code directly within the R environment.

 - [songClip](https://mlvisions.github.io/songClip/): Prototype R package for running a DJ booth! The core `clip_song()` function runs an R shiny app. The app will allow you to import an audio library, choose a specific song (any audio file of similar size), modify sound settings (crop it, create loops, adjust equalizer settings, alter playback speed, etc.), and then save out the modified song. The hope was to eventually support layering tracks, similar to a DJ booth, but that is quite a whiles away.

**Note** that the repositories below are from my college days, when I wasn't nearly as good or organized at coding:). I have additional [repositories](https://github.com/barrettk?tab=repositories) on my GitHub that feature notably higher code quality, including improved code organization, readability, and conciseness. While most of these are currently set to private, I would be happy to provide access to interested parties on a case-by-case basis.

I hope to add more personal apps & R packages in the future!

<hr>



```{r}

ad_text <- "
I modeled the anaerobic digestion of hydraulic fracking contaminants for my senior design project (<a href='https://barrettk.github.io/AnaerobicDigestion/' target='_blank'>see GitHub</a>). The model contains 40+ PDE's describing the advanced biological process and reactor properties. An R shiny dashboard app was constructed to facilitate the adjustment model parameters and reactor settings, allowing for quick simulations and sensitivity analyses. An full-screen instance of the app is hosted <a href='https://kylebarrett.shinyapps.io/AnaerobicDigestion/' target='_blank'>here</a>, but you can view the embedded version below
"

brew_text <- "
<ul>
<li>Here's an example of one of the apps I made for personal use back in the day (Homebrewing!). I used to use it to help me keep track of all the ingredients I liked, determine proper measurements, and estimate the pricing. Never actually sold any, but was glad I learned my profit margins wouldn't be too great.</li>
<li>You can run the app full screen on <a href='https://kylebarrett.shinyapps.io/Kombucha/' target='_blank'>shinyapps.io</a> or check it out on <a href='https://barrettk.github.io/KombuchaBrewing/' target='_blank'>GitHub</a></li>
<ul><li><b>Note:</b> It looks like some formatting features aren't working too great on shinyapps.io. Choosing not to fix it with my refined knowledge for nostalgia:)</li></ul>
</ul>
"

html_style_text <- "
I have developed R Shiny applications with more sophisticated user interfaces using HTML and CSS style sheets. These apps are designed to look and feel like traditional web applications rather than typical R Shiny interfaces. While the prototype I'm currently sharing is not fully functional, it demonstrates my ability to create modern and polished user interfaces for R Shiny apps.
"

fluidRow(
  column(
    width = 12,
    br(), br(),
    shinydashboard::tabBox(
      width = NULL,
      tabPanel(
        "Anaerobic Digestion",
        br(),br(),
        fluidRow(
          column(
            width = 12,
            HTML(ad_text),
            br(),br(),
            tags$iframe(id="AnaerobicDigestion", src="https://kylebarrett.shinyapps.io/AnaerobicDigestion/",
                        style="border: none; width: 1300px; height: 800px; display:inline-block; text-align:center;",
                        frameborder="0")
          )
        ),
        hr(),
        h4("Walkthrough"),
        fluidRow(
          column(
            width = 12, 
            align="center",
            embed_url(AD_Link)
          )
        )
      ),
      tabPanel(
        "Homebrewing",
        br(),br(),
        fluidRow(
          column(
            width = 12,
            HTML(brew_text),
            br(),br(),
            tags$iframe(id="Kombucha App", src="https://kylebarrett.shinyapps.io/Kombucha/",
                        style="border: none; width: 1300px; height: 800px; display:inline-block; text-align:center;",
                        frameborder="0")
          )
        )
      ),
      tabPanel(
        "Custom HTML layouts",
        br(),br(),
        fluidRow(
          column(
            width = 12,
            HTML(html_style_text)
          )
        ),
        br(),
        fluidRow(
          column(
            width = 12, 
            align="center",
            embed_url(EducatR_Link)
          )
        )
      )
    )
  )
)
```


