---

---

<br>
<link rel="stylesheet" href="styles.css" type="text/css">
```{r setup, include=FALSE, echo=FALSE}
library(htmltools)
library(vembedr)
AD_Link <- "https://www.youtube.com/watch?v=Z9XZ7gUKEIQ"
```
## Github Repositories

- I modeled the <a href="https://kylebarrett.github.io/AnaerobicDigestion/" target="_blank">anaerobic digestion of hydraulic fracking contaminants</a> using the R package, [mrgsolve](https://github.com/metrumresearchgroup/mrgsolve). I developed an R shiny dashboard app to adjust model parameters and reactor settings. The deployed version currently does not run, though it should function properly if you run the files locally.
 
```{r echo=FALSE}
embed_url(AD_Link)
```

- Other repositories on my GitHub illustrate some of my early R shiny experience, but are not relevant to other skills/interests i'm attempting to showcase.

## Professional Work

### Certara
 - <a href="https://pharmacometrics.shinyapps.io/COVID-19-VK-MODEL/" target="_blank">Viral Kinetics Model</a>
 - <a href="https://pharmacometrics.shinyapps.io/COVID-19-CompoundScreening_TestNewUI/" target="_blank">Compound Screening Dashboard</a>
  - Note that this link may soon be changed. Will publish the offical Certara link when this happens.
 - I helped develop other apps on <a href="https://www.covidpharmacology.com/in-silico-workbench/" class="uri">Certara's website</a> using the flexdashboard R package, though I wouldnt count this as R shiny experience given the R package's simplicity
 


<video width="320" height="240" controls><source src="EducatR.mp4" type="video/mp4">
  Your browser does not support the video tag.
</video>

