---

---

<br>
<link rel="stylesheet" href="www/css/styles.css" type="text/css">

```{r setup, include=FALSE, echo=FALSE}
library(htmltools)
library(vembedr)
library(shiny)
AD_Link <- "https://www.youtube.com/watch?v=Z9XZ7gUKEIQ"
EducatR_Link <- "https://youtu.be/DUwFSHFnWp8"
```

# Professional Work

### Certara
 - <a href="https://pharmacometrics.shinyapps.io/COVID-19-CompoundScreening_TestNewUI/" target="_blank">Compound Screening Dashboard</a>, which links to other apps I worked on.
   -  Note that this link may soon be changed. Will publish the offical Certara link when this happens.
 - <a href="https://pharmacometrics.shinyapps.io/COVID-19-VK-MODEL/" target="_blank">Viral Kinetics Model</a>
 - I helped develop other apps on <a href="https://www.covidpharmacology.com/in-silico-workbench/"  target="_blank">Certara's website</a> using the flexdashboard R package, though I wouldnt count this as R shiny experience given the R package's simplicity

<hr>

# Github Repositories

**Anaerobic Digestion:**

- I modeled the anaerobic digestion of hydraulic fracking contaminants for my senior design project (<a href="https://kylebarrett.github.io/AnaerobicDigestion/" target="_blank">see GitHub</a>). I used the R package, [mrgsolve](https://github.com/metrumresearchgroup/mrgsolve) to handle the + 40 PDE's describing the advanced biological process and reactor properties. An R shiny dashboard app was constructed to facilitate the adjustment model parameters and reactor settings. The deployed version currently does not run, though it should function properly if you run the files locally. I recorded a video of me using it to illustrate some of the features.

```{r echo=FALSE}
fluidRow(column(12,align="center",embed_url(AD_Link)))
```

- Other [repositories](https://github.com/KyleBarrett?tab=repositories) on my GitHub illustrate some of my early R shiny experience, but are not relevant to other skills/interests i'm attempting to showcase.
<hr>

**EducatR R shiny app**

 - I have made R shiny apps that with more advanced UIs involving HTML and CSS style sheets. You'd never know you were looking at an R shiny app. This app isnt functional, and was only meant as a prototype. However it illustrates my ability to move away from traditional R shiny GUIs.
```{r echo=FALSE}
fluidRow(column(12,align="center",embed_url(EducatR_Link)))
```
<hr>

**Homebrewing**

- Here's an example of one of the apps I've made for personal use (Homebrewing!). I use it to help me keep track of all the ingredients I like, determine proper measurements, and estimate the pricing before I even start!
- https://kylebarrett.shinyapps.io/Kombucha/

<iframe id="Kombucha App" src=" https://kylebarrett.shinyapps.io/Kombucha/"
style="border: none; width: 1000px; height: 800px"
frameborder="0">
</iframe>

<hr>
