---

---

<br>
<link rel="stylesheet" href="www/css/styles.css" type="text/css">

```{r setup, include=FALSE, echo=FALSE}
library(htmltools)
library(vembedr)
library(shiny)
AD_Link <- "https://www.youtube.com/watch?v=Z9XZ7gUKEIQ"
EducatR_Link <- "https://youtu.be/DUwFSHFnWp8"
```

# Professional Work

### Certara
 - <a href="https://pharmacometrics.shinyapps.io/COVID-19-CompoundScreening_TestNewUI/" target="_blank">Compound Screening Dashboard</a>, which links to other apps I worked on.
   -  Note that this link may soon be changed. Will publish the offical Certara link when this happens.
 - <a href="https://pharmacometrics.shinyapps.io/COVID-19-VK-MODEL/" target="_blank">Viral Kinetics Model</a>
 - I helped develop other apps on <a href="https://www.covidpharmacology.com/in-silico-workbench/"  target="_blank">Certara's website</a> using the flexdashboard R package, though I wouldnt count this as R shiny experience given the R package's simplicity

<hr>

# Github Repositories

- I modeled the anaerobic digestion of hydraulic fracking contaminants for my senior design project (<a href="https://kylebarrett.github.io/AnaerobicDigestion/" target="_blank">see GitHub</a>). I used the R package, [mrgsolve](https://github.com/metrumresearchgroup/mrgsolve) to handle the + 40 PDE's describing the advanced biological process and reactor properties. An R shiny dashboard app was constructed to facilitate the adjustment model parameters and reactor settings. The deployed version currently does not run, though it should function properly if you run the files locally. I recorded a video of me using it to illustrate some of the features.

 - **Anaerobic Digestion Preview:**
```{r echo=FALSE}
fluidRow(column(12,align="center",embed_url(AD_Link)))
```

- Other [repositories](https://github.com/KyleBarrett?tab=repositories) on my GitHub illustrate some of my early R shiny experience, but are not relevant to other skills/interests i'm attempting to showcase.
<hr>
- I have made R shiny apps that with more advanced UIs involving HTML and CSS style sheets. You'd never know you were looking at an R shiny app.

 - **EducatR R shiny app:**
```{r echo=FALSE}
fluidRow(column(12,align="center",embed_url(EducatR_Link)))
```

<hr>
