---
output:
  html_document:
    theme: paper
    css:
      # - "../www/css/kb-shiny.css"
      - "../www/css/modest.css"
    common-ext-css:
      - "//use.fontawesome.com/releases/v5.0.6/css/all.css"
date: "`r format(Sys.time(), '%A %B %d, %Y, %I:%M %p %Z')`"
---

<style type="text/css">
.main-container {
max-width: 100% !important;
margin: auto;
}
</style>

```{r setup_links, include=FALSE, echo=FALSE}
suppressPackageStartupMessages({
  library(htmltools)
  library(vembedr)
  library(shiny)
  library(shinycssloaders)
})

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.height = 8, fig.width = 10)

AD_Link <- "https://www.youtube.com/watch?v=Z9XZ7gUKEIQ"
EducatR_Link <- "https://youtu.be/DUwFSHFnWp8"
```


### Professional Work

#### Metrum Research Group
- I have contributed to many of the packages found at <a href="https://github.com/metrumresearchgroup" target="_blank">github.com/metrumresearchgroup</a>, relating to NONMEM model management & submission, data visualization (pmforest, pmplots, etc.), data summarization and formatting (exported as latex, HTML, RTF, or MS word), software validation, and R shiny.
- Each of these packages bundled together facilitate model development and submission, and are outlined in Metrum's [Expo](https://merge.metrumrg.com/expo/expo1-nonmem-foce/).
- Designed and personalized R shiny apps for internal tool development and external client needs, usually relating to PKPD simulation.
- Developed a shiny app to contain re-usable shiny modules, with the intention of creating more portable shiny code to be used in multiple client projects.
- Developed a complex shiny app to sort through and filter a database with interactive visualizations, statistical summaries, and parameterized report generation. 
- Worked on client projects within the scope of data assembly, EDA tables and figures, PK simulation, data visualization and report generation.
- Helped validate and write tests for our cloud computing platform, Metworx.

#### Certara
- <a href="https://pharmacometrics.shinyapps.io/COVID-19-CompoundScreening_TestNewUI/" target="_blank">Compound Screening Dashboard</a>, which links to other apps I worked on.
-  Note that this link may soon be changed. Will publish the offical Certara link when this happens.
- <a href="https://pharmacometrics.shinyapps.io/COVID-19-VK-MODEL/" target="_blank">Viral Kinetics Model</a>
- I helped develop other apps on <a href="https://www.covidpharmacology.com/in-silico-workbench/"  target="_blank">Certara's website</a> using the flexdashboard R package, though I wouldnt count this as R shiny experience given the R package's simplicity




### Github Repositories

**Note** that the repositories below are from my college days, when I wasn't nearly as good or organized at coding:). I have additional [repositories](https://github.com/barrettk?tab=repositories) on my GitHub that feature notably higher code quality, including improved code organization, readability, and conciseness. While most of these are currently set to private, I would be happy to provide access to interested parties on a case-by-case basis.

I hope to add more personal apps & R packages in the future!


```{r}

ad_text <- "
I modeled the anaerobic digestion of hydraulic fracking contaminants for my senior design project (<a href='https://barrettk.github.io/AnaerobicDigestion/' target='_blank'>see GitHub</a>). The model contains 40+ PDE's describing the advanced biological process and reactor properties. An R shiny dashboard app was constructed to facilitate the adjustment model parameters and reactor settings, allowing for quick simulations and sensitivity analyses. An full-screen instance of the app is hosted <a href='https://kylebarrett.shinyapps.io/AnaerobicDigestion/' target='_blank'>here</a>, but you can view the embedded version below
"

brew_text <- "
<ul>
<li>Here's an example of one of the apps I made for personal use back in the day (Homebrewing!). I used to use it to help me keep track of all the ingredients I liked, determine proper measurements, and estimate the pricing. Never actually sold any, but was glad I learned my profit margins wouldn't be too great.</li>
<li>You can run the app full screen on <a href='https://kylebarrett.shinyapps.io/Kombucha/' target='_blank'>shinyapps.io</a> or check it out on <a href='https://barrettk.github.io/KombuchaBrewing/' target='_blank'>GitHub</a></li>
* <b>Note:</b> It looks like some formatting features aren't working too great on shinyapps.io. Choosing not to fix it with my refined knowledge for nostalgia:)
</ul>
"

html_style_text <- "
I have developed R Shiny applications with more sophisticated user interfaces using HTML and CSS style sheets. These apps are designed to look and feel like traditional web applications rather than typical R Shiny interfaces. While the prototype I'm currently sharing is not fully functional, it demonstrates my ability to create modern and polished user interfaces for R Shiny apps.
"

fluidRow(
  column(
    width = 12,
    br(), br(),
    shinydashboard::tabBox(
      width = NULL,
      tabPanel(
        "Anaerobic Digestion",
        br(),br(),
        fluidRow(
          column(
            width = 12,
            HTML(ad_text),
            br(),br(),
            tags$iframe(id="AnaerobicDigestion", src="https://kylebarrett.shinyapps.io/AnaerobicDigestion/",
                        style="border: none; width: 1300px; height: 800px; display:inline-block; text-align:center;",
                        frameborder="0")
          )
        ),
        hr(),
        h4("Walkthrough"),
        fluidRow(
          column(
            width = 12, 
            align="center",
            embed_url(AD_Link)
          )
        )
      ),
      tabPanel(
        "Homebrewing",
        br(),br(),
        fluidRow(
          column(
            width = 12,
            HTML(brew_text),
            br(),br(),
            tags$iframe(id="Kombucha App", src="https://kylebarrett.shinyapps.io/Kombucha/",
                        style="border: none; width: 1300px; height: 800px; display:inline-block; text-align:center;",
                        frameborder="0")
          )
        )
      ),
      tabPanel(
        "Custom HTML layouts",
        br(),br(),
        fluidRow(
          column(
            width = 12,
            HTML(html_style_text)
          )
        ),
        br(),
        fluidRow(
          column(
            width = 12, 
            align="center",
            embed_url(EducatR_Link)
          )
        )
      )
    )
  )
)
```

<!-- **Anaerobic Digestion:** -->

<!-- - I modeled the anaerobic digestion of hydraulic fracking contaminants for my senior design project (<a href="https://barrettk.github.io/AnaerobicDigestion/" target="_blank">see GitHub</a>). The model contains 40+ PDE's describing the advanced biological process and reactor properties. An R shiny dashboard app was constructed to facilitate the adjustment model parameters and reactor settings, allowing for quick simulations and sensitivity analyses. An full-screen instance of the app is hosted <a href="https://kylebarrett.shinyapps.io/AnaerobicDigestion/" target="_blank">here</a>, but you can view the embedded version below: -->



<!-- <iframe id="AnaerobicDigestion" src=" https://kylebarrett.shinyapps.io/AnaerobicDigestion/" -->
<!-- style="border: none; width: 1300px; height: 800px; display:inline-block; text-align:center;" -->
<!-- frameborder="0"> -->
<!-- </iframe> -->



<!-- # ```{r AD, echo=FALSE} -->
<!-- # fluidRow(column(12,align="center",embed_url(AD_Link))) -->
<!-- # ``` -->


<!-- <hr> -->

<!-- **EducatR R shiny app** -->

<!-- - I have developed R Shiny applications with more sophisticated user interfaces using HTML and CSS style sheets. These apps are designed to look and feel like traditional web applications rather than typical R Shiny interfaces. While the prototype I'm currently sharing is not fully functional, it demonstrates my ability to create modern and polished user interfaces for R Shiny apps. -->
<!-- # ```{r idk, echo=FALSE} -->
<!-- # fluidRow(column(12,align="center",embed_url(EducatR_Link))) -->
<!-- # ``` -->

<!-- <hr> -->

<!-- **Homebrewing** -->

<!-- * Here's an example of one of the apps I made for personal use back in the day (Homebrewing!). I used to use it to help me keep track of all the ingredients I liked, determine proper measurements, and estimate the pricing. Never actually sold any, but was glad I learned my profit margins wouldn't be too great. -->
<!-- * You can run the app full screen on [shinyapps.io](https://kylebarrett.shinyapps.io/Kombucha/) or check it out on [GitHub](https://kylebarrett.github.io/KombuchaBrewing/) -->
<!-- * <b>Note:</b> It looks like some formatting features aren't working too great on shinyapps.io. Choosing not to fix it with my refined knowledge for nostalgia:) -->


<!-- <iframe id="Kombucha App" src=" https://kylebarrett.shinyapps.io/Kombucha/" -->
<!-- style="border: none; width: 1300px; height: 800px; display:inline-block; text-align:center;" -->
<!-- frameborder="0"> -->
<!-- </iframe> -->

<!-- <hr> -->

