---
output: 
  html:
    css: "assets/css/styles_quarto.css"
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ".",
  echo = FALSE)
library(htmltools)
library(fontawesome)
library(dplyr)

func_dir <- here::here("functions")
functions <- list.files(func_dir)
for(function.i in functions){
  source(file.path(func_dir, function.i))
}

app_url <- "https://kylebarrett.shinyapps.io/AnaerobicDigestion/"
```

<!-- For RMD: -->
<!-- # Anaerobic Digestion {.tabset .tabset-fade .tabset-pills} --> 

### Anaerobic Digestion 


```{r results="asis"}
 create_fullscreen_btn(app_url)
```


::: {.panel-tabset}

## Description
#### Background

I modeled the anaerobic digestion of hydraulic fracking contaminants for my senior design project (<a href='https://barrettk.github.io/AnaerobicDigestion/' target='_blank'>see GitHub</a>). The model contains 40+ PDE's describing the advanced biological process and reactor properties. An R shiny dashboard app was constructed to facilitate the adjustment model parameters and reactor settings, allowing for quick simulations and sensitivity analyses.


```{r}
#| output: asis
 prev_str <- paste("## App Preview", fa("tablet-screen-button", fill = "#15b1bf"))
 cat(prev_str)
```


```{r}
#| column: screen-inset-shaded
embedd_app(app_url)
```


:::
