---
output: 
  html:
    css: "assets/css/styles_quarto.css"
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ".",
  echo = FALSE)
library(htmltools)
library(fontawesome)
library(dplyr)

func_dir <- here::here("functions")
functions <- list.files(func_dir)
for(function.i in functions){
  source(file.path(func_dir, function.i))
}

app_url <- "https://kylebarrett.shinyapps.io/Kombucha/"
```

<!-- For RMD: -->
<!-- # Homebrewing {.tabset .tabset-fade .tabset-pills} --> 

### Homebrewing 


```{r results="asis"}
 create_fullscreen_btn(app_url)
```


::: {.panel-tabset}

## Description
#### Background

Here's an example of one of the apps I made for personal use back in the day (Homebrewing!). I used to use it to help me keep track of all the ingredients I liked, determine proper measurements, and estimate the pricing. Never actually sold any, but was glad I learned my profit margins wouldn't be too great.

- Feel free to check it out on <a href='https://barrettk.github.io/KombuchaBrewing/' target='_blank'>GitHub</a>!
   - **Note:** It looks like some formatting features aren't working too great on `shinyapps.io`, and some dropdowns don't work correctly in the embedded version here. Choosing not to fix it at the moment, though the full screen version should operate a bit more smoothly.


```{r}
#| output: asis
 prev_str <- paste("## App Preview", fa("tablet-screen-button", fill = "#15b1bf"))
 cat(prev_str)
```


```{r}
#| column: screen-inset-shaded
embedd_app(app_url)
```


:::
